\LARGE \bf Approximately Orchestrated Road Traffic Automata\\ a General Traffic Simulation Framework

### 2012-03-10 papers/itsc_2012/final.tex
diagnosing epsilon issue
seeing if things are even possible...

\commentd{upgrading stop signs to signals, optimizing timing?}

>>>>

controlled factors: several maps, agent spawning pattern
independent: every intersection has 1 of 3 main policies, each can have tweaks
output: average/total/whatever wasted time and intersection thruput

key: all of this code is separated out, easy to edit, 200 lines. even if results
suck, thats fine, we'll work on em. different results in diff places is maybe
even good! one size doesnt fit all, suggests we need a mix and some adapting to
maps. future experiment could be upgrading few at a time.
